---
title: "Assignment 5 - Meta-analysis of pitch in schizophrenia"
author: "Riccardo Fusaroli"
date: "3/7/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Building on the shoulders of giants: meta-analysis

## Questions to be answered

1. What is the current evidence for distinctive vocal patterns in schizophrenia? Report how many papers report quantitative estimates, comment on what percentage of the overall studies reviewed they represent (see PRISMA chart) your method to analyze them, the estimated effect size of the difference (mean effect size and standard error) and forest plots representing it. N.B. Only measures of pitch mean and pitch sd are required for the assignment (all the other measures have been removed from the dataset for the sake of simplicity). 

2. Do the results match your own analysis from Assignment 3? If you add your results to the meta-analysis, do the estimated effect sizes change? Report the new estimates and the new forest plots.

3. Assess the quality of the literature: report and comment on heterogeneity of the studies (tau, I2), on publication bias (funnel plot), and on influential studies.

## Tips on the process to follow:

- Download the data on all published articles analyzing voice in schizophrenia and the prisma chart as reference of all articles found and reviewed
Data: https://www.dropbox.com/s/0l9ur0gaabr80a8/Matrix_MetaAnalysis_Diagnosis_updated290719.xlsx?dl=0
Prisma chart: https://www.dropbox.com/s/vbjf6ff73dv9tru/PRISMA%202009%20flow%20diagram_PP.pptx?dl=0 
- Look through the dataset to find out which columns to use, and if there is any additional information written as comments (real world data is always messy!).
    * Hint: PITCH_F0M and PITCH_F0SD group of variables are what you need
- Following the procedure in the slides calculate effect size and standard error of the effect size per each study. N.B. we focus on pitch mean and pitch standard deviation.
 . first try using lmer (to connect to what you know of mixed effects models)
 . then use rma() (to get some juicy additional statistics)

- Build a forest plot of the results (forest(model))
 
- Go back to Assignment 3, add your own study to the data table, and re-run meta-analysis. Do the results change?

- Now look at the output of rma() and check tau and I2

```{r Loading data}
# Load data:
data <- readxl::read_xlsx("Matrix_MetaAnalysis_Diagnosis_updated290719.xlsx")
head(data)

# Find which columns to use:

# Does the hint mean that we use columns "PITCH_F0_HC_M", "PITCH_F0_HC_SD", "PITCH_F0_SZ_M", and "PITCH_F0_SZ_SD"?
  # that would make sense sine HC like stands for healthy control and SZ for schizophrenic.
  # and our pitch in assignment 3 was called F0
  # Does that mean we don't care about all the other F's? (e.g. PITCH_F4_HC_M) - and what about 'PITCH_FORAN_SZ_SD'?
# Additional information is in column 'pitch_f0_variability' where it says maybe how pitch (variability) was measured?
  # the column 'frequency' notes in what measure the frequencies are (e.g. hz or semitones)
```

```{r Procedure from slides}
# What does "calculate effect size and standard error of the effect size per each study" mean?
  # does it mean calculate mean effect size of all studies compiled together and the SE to go with that mean? (why not SD?)
  # does it mean using metafor::escalc() to calculate effect sizes (as cohen's d) and their variance? (https://rstudio-pubs-static.s3.amazonaws.com/10913_5858762ec84b458d89b0f4a4e6dd5e81.html)

# See lecture 11-12 code for this:
library(metafor)
data <- escalc(measure = "SMD", #SMD stands for standardized mean difference AKA Cohen's d
               n1i = SAMPLE_SIZE_HC, n2i = SAMPLE_SIZE_SZ,
               m1i = PITCH_F0_HC_M, m2i = PITCH_F0_SZ_M,
               sd1i = PITCH_F0_HC_SD, sd2i = PITCH_F0_SZ_SD, data = data)

# the two new columns: (yi = observed effect size, vi = variance)
#View(data$yi)
#View(data$vi)
# standard error would be sei (see: help page for escalc)
```

```{r Making models}
# using lmer
m <- lme4::lmer(yi ~ 1 + (1 | StudyID), weights = 1/vi, data=data, control=lme4::lmerControl(check.nobs.vs.nlev="ignore", check.nobs.vs.nRE="ignore"))

# using rma
m1 <-rma(yi, vi, data = data, slab = StudyID)
forest(m1)

# the numbers on the left of the forest plot is yi

```

```{r Adding our PF3 to the data set}
df_withus <- readxl::read_xlsx("MetaAnalysis_withourassignment3.xlsx")

df_withus <- escalc(measure = "SMD", #SMD stands for standardized mean difference AKA Cohen's d
               n1i = SAMPLE_SIZE_HC, n2i = SAMPLE_SIZE_SZ,
               m1i = PITCH_F0_HC_M, m2i = PITCH_F0_SZ_M,
               sd1i = PITCH_F0_HC_SD, sd2i = PITCH_F0_SZ_SD, data = df_withus)

m2 <-rma (yi, vi, data = df_withus, slab = StudyID)
forest(m2)
forest(m1)

# the square in the forest plot is the weight of that study (study 51, which is ours, seems to be influential)

# https://en.wikipedia.org/wiki/Forest_plot
```

```{r Now look at the output of rma() and check tau and I2}
summary(m1) # tau = 0.2668, I^2 = 50.29%
summary(m2) # tau = 0.2240, I^2 = 55.49%
```

```{r Funnel plot/publication bias}
funnel(m1) # without us
funnel(m2) # with us (notice change in x-axis)

# Generally about the interpreation of funnel plots:  https://www.statisticshowto.com/funnel-plot/
# y-axis:
  # SE of 0 is at the top, studies with lower SE are at the top, higher powered studies are at the top
# x-axis:
  # The line in the middle is the SMD (-0.16 and -0.09), the points are the effect sizes of individual studies
```

```{r Influential studies}

```

